\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-24 tex/ms.tex
force date to be April 1

The bottom panel of Figure~\ref{fig:map} shows the corrected surface
reflectance obtained from the
Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite. The 
image shows the corrected surface reflectance in the I1 band of the instrument,
averaged over the 28 days of data analyzed in this work, and weighted by the
\tess visibility as in the top panel.
The I1 band extends from 0.6 to 0.68 $\mu\mathrm{m}$
\footnote{\url{http://rammb.cira.colostate.edu/projects/npp/VIIRS_bands_and_bandwidths.pdf}},
and therefore covers only about one-fourth of the bandpass of \tess
(nominally 0.6 - 1.0 $\mu\mathrm{m}$).

>>>>

The bottom panel of Figure~\ref{fig:map} shows the corrected surface
reflectance obtained from the
Visible Infrared Imaging Radiometer Suite (\emph{VIIRS}) instrument aboard the 
Suomi National Polar-orbiting Partnership (\emph{Suomi NPP}) satellite
\footnote{Data obtained via 
\href{https://github.com/rodluger/earthshine/blob/master/tex/figures/viirs.sh}{this wget script}.}. 
The image shows the corrected surface reflectance in the I1 band of the instrument,
averaged over the 28 days of data analyzed in this work, smoothed with a Gaussian
filter, and weighted by the \tess visibility as in the top panel.
The I1 band extends from 0.6 to 0.68 $\mu\mathrm{m}$
\footnote{\url{http://rammb.cira.colostate.edu/projects/npp/VIIRS_bands_and_bandwidths.pdf}},
and therefore covers only about one-fourth of the bandpass of \tess
(nominally 0.6 - 1.0 $\mu\mathrm{m}$).
